\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-08-05 popl-2019-journal-v/discussion.tex
[POPLjv] Rephrase sentence

  We have not investigated support for continuations and exceptions in \stktokens{} thoroughly but believe they are supported.
  The continuations and exceptions could plausibly be implemented similarly to return pointers, i.e.\ as sealed code capabilities.
  The exception capability would point to a piece of code handling the specific exception, and one would cast an exception by invoking the exception capability.
  The continuations and exceptions would be sealed with the return capability allowing them to be used with the appropriate encapsulated stack frame.
  The stack is crucial to \stktokens{}, and it must be unravelled as an exception falls through calls.
  One way to handle stack unravelling is to make the code responsible for unravelling its own stack frame.
  For a piece of code that wants to pass on a continuation, it would have to pass on a capability for a piece of code that unravels the stack and uses the continuation.
  Alternatively, it may be possible to have a piece of central trusted code that does the stack unravelling.

>>>>

  We have not investigated support for continuations and exceptions in \stktokens{} thoroughly but believe they are supported.
  The continuations and exceptions could plausibly be implemented similarly to return pointers, i.e.\ as sealed code capabilities.
  The exception capability would point to a piece of code handling the specific exception, and one would cast an exception by invoking the exception capability.
  The continuations and exceptions would be sealed with the return capability allowing them to be used with the appropriate encapsulated stack frame.
  The stack is crucial to \stktokens{}, and it must be unravelled as an exception falls through calls.
  One way to handle stack unravelling is to make the code responsible for unravelling its own stack frame.
  To pass on a continuation, it would have to be wrapped in some sort of continuation forward record that unravels the stack and calls the continuation.
  Alternatively, it may be possible to have a piece of central trusted code that does the stack unravelling.
